### 2013-02-15 doc/icml2013/model.tex

The mixture of linear regressions model \citep{VieleTong2002} defines
a conditional distribution over a response $y \in \Re$
given covariates $x \in \Re^d$.
The generation of $y$ given $x$ involves two steps:
(i) draw the mixture component $h \in [K]$ according to mixture proportions
$\pi = (\pi_1, \dots, \pi_K)$;
and (ii) generate $y$ from a Gaussian centered at $\beta_h^\top x$ with
variance $\sigma^2$.
%Given $x$, the generative process for the response
%variables is,
\begin{eqnarray*}
  h &\sim& \mult(\pi), \\
  y \mid h &\sim& \normal{ \beta_{h}^T x}{ \sigma^2 }.
\end{eqnarray*}
%where $h$ is a latent variable corresponding to the mode.
The parameters of the model are $\theta = (\pi, B, \sigma^2)$,
where $\pi \in \Re^d$ are the mixture proportions,
$B = [\beta_1 \mid \dots \mid \beta_K] \in \Re^{d \times K}$,
are the regression coefficients,
and $\sigma^2$ is the variance of the observation noise.
The learning problem is stated as follows:
given $N$ i.i.d. samples $(\xn{1}, \yn{1}), \dots, (\xn{N}, \yn{N})$
drawn from the model with some unknown parameters $\theta^*$,
return an estimate of the parameters $\hat\theta$.

>>>>

The mixture of linear regressions model \citep{VieleTong2002} defines
a conditional distribution over a response $y \in \Re$
given covariates $x \in \Re^d$.
The generation of $y$ given $x$ involves two steps:
(i) draw the mixture component $h \in [K]$ according to mixture proportions
$\pi = (\pi_1, \dots, \pi_K)$;
and (ii) generate $y$ from a Gaussian centered at $\beta_h^\top x$ with
variance $\sigma^2$.
%Given $x$, the generative process for the response
%variables is,
\begin{eqnarray*}
  h &\sim& \mult(\pi), \\
  y \mid h &\sim& \normal{ \beta_{h}^T x}{ \sigma^2 }.
\end{eqnarray*}
%where $h$ is a latent variable corresponding to the mode.
The parameters of the model are $\theta = (\pi, B, \sigma^2)$,
where $\pi \in \Re^d$ are the mixture proportions,
$B = [\beta_1 \mid \dots \mid \beta_K] \in \Re^{d \times K}$
are the regression coefficients,
and $\sigma^2$ is the variance of the observation noise.
The learning problem is stated as follows:
given $N$ i.i.d. samples $(\xn{1}, \yn{1}), \dots, (\xn{N}, \yn{N})$
drawn from the model with some unknown parameters $\theta^*$,
return an estimate of the parameters $\hat\theta$.
